Detecting Facial Expressions in Professional Tennis Matches

### 2017-03-03 Report06-12.Rmd
Regression added to report
Updated to include optimising Regression results and comments in report

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalcik"
date: "13 February 2017"
output: bookdown::pdf_document2
fontsize: 11pt
documentclass: article
bibliography: references.bib
---

@@

Regression analysis showed that the situation attribute of an image was most influential in increasing the likelihood of a hit.
And head angle was most influential in decreasing.

```{r}
# Prepare data
library(purrr)
library(dplyr)
library(ggplot2)
hitmiss <- function(x){
  allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
  hit <- allType %in% x$type
  x[1,] %>%
    dplyr::select(file:visorhat) %>%
    cbind(type = allType, hit = hit)
}

glmFits <- ALLmetaIMGFaces %>%
  split(.$FaceKey) %>%
  map_df(~ hitmiss(.)) %>%
  split(.$type) %>%
  map(~ glm(hit ~ . + visorhat*glasses, data = select(., -type, -file), binomial(link = "logit")))

glmSummary <- glmFits %>%
  map(~ rename(cbind(rownames_to_column(cbind(as.data.frame(coef(summary(.)))))), variable = rowname))

glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary)))

@@

```{r, Regression-Significance-Plot, fig.cap = "\\label{Regression--Significance-Plot}"}
## Significance of variables by software
glmPlot %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
  ggplot(aes(x=type, y=`Pr(<|z|)`)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  geom_col(aes(fill=significant)) + 
  facet_wrap(~ variable)
```

The bar chart of the interaction of Glasses and Visors in \@ref(Regression--Significance-Plot) or Hats shows that when the face is accessorised with both, Google has a significantly increased chance of finding the face

```{r, Regression-Estimates-Plot, fig.cap = "\\label{Regression--Estimates-Plot}"}
## Significance of Estimated variable influences by software
glmPlot %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  ggplot(aes(x=type, y=Estimate)) + 
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  geom_col(aes(fill=significant)) + 
  facet_wrap(~ variable, scales = "free_y")

#parallel coordinate plot, vars on x????
#unpack intercept
#don't force to zero
#convert into full model decription - every single level combination
#have every level and cross level - order combinations by p value
#function for estimates for each treatment
#multinomail 
#add hit or miss column, to utilise caret package
```

```{r Regression-Situation-Table, fig.cap = "\\label{Regression-Situation-Table}"}

RegSituation<-glmPlot %>% subset(grepl("situation*", variable)) %>% select(variable, Estimate, type)

#RegSituation

data_wide <- spread(RegSituation, variable, Estimate)

names(data_wide)[names(data_wide)=="situationCourt player close-up"] <- "Court player close-up"
names(data_wide)[names(data_wide)=="situationCrowd"] <- "Crowd"
names(data_wide)[names(data_wide)=="situationOff court close up of player"] <- "Off court close up of player"
names(data_wide)[names(data_wide)=="situationCourt close-up not player"] <- "Court close-up not player"

kable(data_wide, format = "markdown", booktabs = TRUE, caption = "")
```

```{r Regression-Angle-Table, fig.cap = "\\label{Regression-Angle-Table}"}

RegHeadAngle<-glmPlot %>% subset(grepl("headangle*", variable)) %>% select(variable, Estimate, type)

#RegSituation

data_wideHead <- spread(RegHeadAngle, variable, Estimate)

names(data_wideHead)[names(data_wideHead)=="headangleOther"] <- "Other"
names(data_wideHead)[names(data_wideHead)=="headangleProfile"] <- "Profile"

kable(data_wideHead, format = "markdown", booktabs = TRUE, caption = "")
```

>>>>

---
title: "Detecting Facial Expressions in Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalcik"
date: "13 February 2017"
output: bookdown::pdf_document2
fig_caption: yes
fontsize: 11pt
documentclass: article
bibliography: references.bib
link_citations: yes
---

@@

Regression analysis showed that the situation variable had significant differences between all levels and the interecept level of "Court in Play".

 The bar charts of the situations show that the situation is important in influencing the detection of a face. When the face is accessorised with them, all softwares have a significantly increased chance of finding the face in comparison to the base rate category of the "Court in Play". While the image being a Graphic had a large impact it was not significant, this is likely because of the small number of images with this attribute. It also shows that the shot angle is only significant for one or two softwares at each level.

```{r Regression, fig.height=9.5, fig.width=7.5, fig.cap = "\\label{Regression} "}
# Prepare data
library(purrr)
library(tidyverse)
library(gridExtra)
library(dplyr)
library(ggplot2)

hitmiss <- function(x){
  allType <- c("Animetrics", "Google", "Microsoft", "Skybiometry")
  hit <- allType %in% x$type
  x[1,] %>%
    dplyr::select(file:visorhat) %>%
    cbind(type = allType, hit = hit)
}

GlmModelCreation <- function(model, data = ALLmetaIMGFaces) {
  glmFits <- data %>% 
  split(.$FaceKey) %>% 
  map_df(~ hitmiss(.)) %>% 
  split(.$type) %>% 
  map(~ glm(model, data = dplyr::select(., -type, -file, -boxID), binomial(link = "logit")))
}

ConvertModel2Table <- function(model){
  model %>%
    summary %>%
    coef %>%
    as.data.frame %>%
    cbind %>%
    rownames_to_column %>%
    cbind %>%
    dplyr::rename(variable = rowname)
}

GlmModelEstimates <- function(model, data = GlmModelCreation(model)){
  glmSummary <- data %>% 
    map(~ ConvertModel2Table(.))

  glmPlot <- do.call(rbind, Map(cbind, glmSummary, type = names(glmSummary))) 
  return(glmPlot)
}

SignificancePlot <- function(model, data = GlmModelEstimates(model)) {
  data %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  mutate(`Pr(<|z|)` = 1 - `Pr(>|z|)`) %>%
  ggplot(aes(x=type, y=`Pr(<|z|)`)) +  
  theme(axis.text.x = element_text(angle = 30, hjust = 1)) +
  geom_col(aes(fill=significant)) + 
  facet_wrap(~ variable)
}

EstimatesPlot <- function(model, data = GlmModelEstimates(model)) {
  data %>%
  mutate(significant = `Pr(>|z|)` < 0.05) %>%
  ggplot(aes(x=type, y=Estimate)) +  
  theme(axis.text.x = element_text(angle = 30, hjust = 1), 
        axis.text.y = element_text(angle = 30, hjust = 1)) +
  geom_col(aes(fill=significant)) + 
  facet_wrap(~ variable, scales = "free_y")
}

ModelPlotResults<-function(model, data = GlmModelEstimates(model)){
  ep<-EstimatesPlot(model, data)
  sp<- SignificancePlot(model, data)
  grid.arrange(ep, sp)
}

ModelPlotResults(hit ~ shotangle + bg + bg*shotangle + graphic + situation + lighting + glasses + visorhat)

@@

A stepwise method was used to determin the best regression model for predicting a hit or miss. The regression model that provided the best AIC, included the scene attributes: Shot Angle, Back Ground, the interaction between these two; whether the scene was a graphic, and the situation on the court when the image was taken.
It also included the lighting on the particular face, and whether the specific face was accessorised with Glasses and a Visor or Hat.
